Title

### 2013-02-23 inc/model_results/lens_charge/lens_charge.tex
more improvements to lens_charge plot

\begin{figure}
  \centering
  \subfloat[][] {
    \label{fig:focus_lens_charge_long}
    \input{lens_60mm}
  }
  \\
  \subfloat[][] { 
    \label{fig:focus_lens_charge_short}
    \input{lens_6mm}
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    Focal behavior of perfect magnetic lenses predicted by the AG model (with DC acceleration voltage of 20kV) as a function of pulse charge $N$.
    Pulses begin at the lens' front focal plane with HW1/eM width $ 500 \mu \text{m}$ and duration 500 fs at 20 kV velocity ($c/3$) or ellipticiy $ \xi ( 0 ) = 0.1 $ (prolate).
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth, \subref{fig:focus_lens_charge_long} $f = $ 60mm and \subref{fig:focus_lens_charge_short} $ f = $ 6.35mm.
    A logarithmic scale is used for comparative clarity.
  }
  \label{fig:focus_lens_charge}
\end{figure}

>>>>

\begin{figure}
  \centering
  \centerline{
    \subfloat[][] {
      \label{fig:focus_lens_charge_long}
      \input{lens_60mm}
    }
    \subfloat[][] { 
      \label{fig:focus_lens_charge_short}
      \input{lens_6mm}
    }
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$.
    Pulses begin at the lens' front focal plane with HW1/eM width $ 500 \mu \text{m}$ and duration 500 fs at 20 kV velocity ($c/3$) for an ellipticiy $ \xi ( 0 ) = 0.1 $ (prolate).
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth, \subref{fig:focus_lens_charge_long} $f = $ 60mm and \subref{fig:focus_lens_charge_short} $ f = $ 6.0mm.
    A logarithmic scale is used for comparative clarity.
  }
  \label{fig:focus_lens_charge}
\end{figure}
